SSA based global code motion of identical computations

### 2017-04-15 hoist.tex
add parse-stat script to parse llvm stats

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
Number of spills                &base   &code-motion &\%loss \\\hline
400.perlbench	&2542	&2481	&0.97\\\hline
401.bzip2	        &718	&707	&0.98\\\hline
403.gcc	        &5778	&5710	&0.98\\\hline
429.mcf	        &14	&17	&1.21\\\hline
433.milc	        &616	&624	&1.01\\\hline
444.namd	        &3185	&3223	&1.01\\\hline
445.gobmk	        &2166	&2170	&1.00\\\hline
447.dealII	        &10038	&9151	&0.91\\\hline
450.soplex	        &1104	&1114	&1.00\\\hline
453.povray	        &5199	&5176	&0.99\\\hline
456.hmmer	        &1195	&1195	&1   \\\hline
458.sjeng	        &168	&169	&1.00\\\hline
462.libquantum	&183	&183	&1   \\\hline
464.h264ref	&3382	&3423	&1.01\\\hline
470.lbm	        &30	&30	&1   \\\hline
471.omnetpp	&521	&522	&1.00\\\hline
473.astar	        &176	&196	&1.11\\\hline
482.sphinx3	&603	&594	&0.98\\\hline
483.xalancbmk	&5101	&4941	&0.96\\\hline
Grand Total	                &42719	&41626	&0.97\\\hline
    \end{tabular}
  \end{center}
  \caption{Number of spills on SPEC2006}
  \label{tab:code-size}
\end{table}
